\documentclass{beamer}
\usetheme{Dresden}

% Packages
\usepackage[utf8]{inputenc} % Handling UTF-8 text
\usepackage[T1]{fontenc}    % Font encoding

%  REFERENCING
% BIBLIOGRAPHY - BIBTEX
\usepackage[sort,round]{natbib} %For the bibliography.
\bibliographystyle{abbrvnat} %Reference style.

% BIBLIOGRAPHY - BIBLATEX
\usepackage[
backend=biber,
style=apa,
bibstyle=authoryear,
citestyle=authoryear,
maxcitenames=2,
maxbibnames=99
]{biblatex}

\setlength\bibitemsep{1\itemsep} % spacing between entries in references
\addbibresource{references.bib} % .bib file


\usepackage{hyperref} %Must be loaded at the end.
\hypersetup{ %Setup of the reference links.
     colorlinks=false,
     linkcolor=black,
     citecolor=black,
     filecolor=black,
     urlcolor=black
}

\usepackage[nameinlink,capitalize]{cleveref} %For the command \cref, load after hyperref.


% Title and other information for the title page
\title{Momentum Strategy Analysis}
\author{Avduli, Müller, Kuljanin, Sherifi}
\date{December 11, 2024}
\institute{University of Zurich}

\begin{document}

\begin{frame}
    \titlepage
\end{frame}

\begin{frame}{Outline}
    \tableofcontents
\end{frame}

\section{Abstract}
\begin{frame}{Abstract}

\end{frame}

\section{Introduction}
\begin{frame}{What is our project about}
    Beamer is a powerful class for creating presentations in LaTeX.
    \begin{itemize}
        \item Lookback 6 was analyzed 
        \item Professional slides
        \item Supports animations and transitions
    \end{itemize}
\end{frame}

\section{Details}
\begin{frame}{Detailed Analysis}
    \begin{itemize}
        \item Analysis 1: Details of the first part of the study.
        \item Analysis 2: Insights into the secondary phase.
        \item Analysis 3: Conclusions drawn from the data.
    \end{itemize}
\end{frame}

\section{Conclusion}
\begin{frame}{Conclusion}
    \begin{itemize}
        \item Major findings: Summary of the key outcomes.
        \item Implications: What these findings mean for the field.
        \item Future work: Next steps in research.
    \end{itemize}
    Thank you for your attention! Any questions?
\end{frame}

\section{References}
\begin{frame}{References}
    \printbibliography
\end{frame}

\end{document}